---
title: "HittersAnalytics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HittersAnalytics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

The 'HittersAnalytics' package provides tools for analyzing the 'Hitters' dataset from the 'ISLR' package, which contains information on the performance and salaries of baseball players. With 'HittersAnalytics' you can: 

- Summarize specific variables. 
- Find the top 10 players by a chosen variable. 
- Calculate correlations between two variables. 
- Create scatterplots to visualize relationships between two variables. 

This vignette demonstrates how to use the package's functions effectively. 

This vignette provides an introduction to the `HittersAnalytics` package.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

options(repos = c(CRAN = "https://cran.rstudio.com"))

```

# Getting Started 

Before using the package, install and load the necessary libraries and dataset. 

```{r getting started}

# Install required packages
install.packages(c("knitr", "rmarkdown", "ISLR", "devtools"))

# Install the HittersAnalytics package from GitHub
devtools::install_github("philinevbekkum/HittersAnalytics")

# Load the libraries
library(HittersAnalytics)
library(ISLR)

# Load the Hitters dataset
data(Hitters)

```

# Example Usage 

Below are examples of how to use the functions in the 'HittersAnalytics' package. You can replace the variable names in these examples with any clumn from the 'Hitters' dataset. 

```{r example usage}

# Summarize the Salary variable
summarize_variable(Hitters, "Salary")

# Find the top 10 players by Runs
top_players <- top_10_variable(Hitters, "Runs")
head(top_players)

# Calculate the correlation between Years and Hits
correlation <- calculate_correlation(Hitters, "Years", "Hits")
correlation

# Create a scatterplot of Years vs. Hits
scatterplot("Years", "Salary")

```

